---
title: "Market and Macros"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: journal
---

```{r setup, include=FALSE}

```

```{r, include=FALSE}
source("final codes.R", local = knitr::knit_global())
```


Employment {data-navmenu="Labor" data-orientation=rows}
=======================================================================

Column 
-----------------------------------------------------------------------

### **Employment-population ratio and participation rate**

```{r,message=FALSE,warning=FALSE}

hchart(lb2[which(lb2$title1 %in% c("Employment-population ratio","Civilian labor force participation rate")),], "line", hcaes(x = date, y =value, group = title1))%>%
  hc_yAxis(title="")%>%
  hc_xAxis(title="")%>% 
  hc_title(text = "")%>%
  hc_navigator(enabled=TRUE)%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")%>%
  hc_add_theme(hc_theme_google())

```


### **Employed & Unemployed**

```{r,message=FALSE,warning=FALSE}

hchart(lb2[which(lb2$title1 %in% c("Unemployed","Employed")),], "line", hcaes(x = date, y =value, group = title1))%>%
  hc_yAxis(title="")%>%
  hc_xAxis(title="")%>% 
  hc_title(text = "")%>%
  hc_navigator(enabled=TRUE)%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")%>%
  hc_add_theme(hc_theme_google())

```

### **Special U Rates**


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(lb4 %>% filter(seriesID=="LNS13025670"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(lb4 %>% filter(seriesID=="LNS14023621"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(lb4 %>% filter(seriesID=="LNS14000000"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(lb4 %>% filter(seriesID=="LNS13327707"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(lb4 %>% filter(seriesID=="LNS13327708"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(lb4 %>% filter(seriesID=="LNS13327709"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  )%>%
  hc_tooltip(headerFormat = "{point.title}",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```

Column 
-----------------------------------------------------------------------
### **Quitting and Hiring, selected months**

```{r,message=FALSE,warning=FALSE}

f1<-list(family="Times New Roman",color = "black")

plot_ly(lb31,x=~date,y=~value,type='bar', color=~title1,colors = c("#D95F02", "#7570B3"))%>% 
  layout(yaxis = list(title = ""), xaxis = list(showgrid = FALSE,title = ""),font=f1)%>%
  config(displayModeBar = FALSE)

```


### **Monthly Quitting, selected Industries(level)**

```{r,message=FALSE,warning=FALSE}

hchart(lb32, "line", hcaes(x = date, y =value, group = title1))%>%
  hc_yAxis(title="")%>%
  hc_xAxis(title="")%>% 
  hc_title(text = "")%>%
  hc_navigator(enabled=TRUE)%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" 
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")%>%
  hc_rangeSelector(enabled = TRUE,selected =4,inputDateFormat= "%b-%y")
  

```


### **Delta:change from Feb20 and Apr20 to September22**
```{r,message=FALSE,warning=FALSE}

plot_ly(lb101, color = I("black")) %>%
  add_segments(x = ~deltaFeb20, xend = ~deltaApr20, y = ~title1, yend = ~title1, showlegend = FALSE) %>%
  add_markers(x = ~deltaFeb20, y = ~title1, name = "deltaFeb20", color = I("brown4")) %>%
  add_markers(x = ~deltaApr20, y = ~title1, name = "deltaApr20", color = I("blue")) %>% 
  layout(  title = "",   xaxis = list(title = "numbers (in thousands)"), margin = list(l = 65))%>%
  layout(yaxis = list(title = ""), xaxis = list(title = ""), barmode = 'stack',showlegend = TRUE,font=f1)%>%
  config(displayModeBar = FALSE)

```


JOLTS {data-navmenu="Labor" data-orientation=rows}
=======================================================================

Column 
-----------------------------------------------------------------------
### **Unemployed per job opening vs. Unemployment(rate)**

```{r}
plot0<-bind_rows(jolt_rate[which(jolt_rate$seriesID=="JTS000000000000000UOR"),],lb4[which(lb4$seriesID=="LNS14000000"),])

```


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(plot0 %>% filter(seriesID=="JTS000000000000000UOR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(plot0 %>% filter(seriesID=="LNS14000000"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" 
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```

### **Quits vs. Hire (level)**


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS000000000000000HIL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS000000000000000QUL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" 
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```


### **Total nonfarm hires and separations rates**


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000HIR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000LDR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000OSR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000QUR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000TSR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```

Column 
-----------------------------------------------------------------------

### **Job openings, hires, and separations levels**


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS000000000000000JOL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS100000000000000JOL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS900000000000000JOL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS000000000000000TSL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS100000000000000TSL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_level %>% filter(seriesID=="JTS900000000000000TSL"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_rangeSelector(enabled = TRUE,selected =4,inputDateFormat= "%b-%y")%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```


### **Job openings, hires, and separations rates**


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000HIR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE) %>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS100000000000000HIR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS900000000000000HIR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS100000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS900000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS000000000000000TSR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS100000000000000TSR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS900000000000000TSR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_rangeSelector(enabled = TRUE,selected =4,inputDateFormat= "%b-%y")%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```

### **Job openings rates by selected industry**


```{r,message=FALSE,warning=FALSE}

  highchart() %>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS110099000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE) %>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS230000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS300000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS510000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS510099000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS520000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=FALSE)%>%
  hc_add_series(jolt_rate %>% filter(seriesID=="JTS700000000000000JOR"),"line", hcaes(x = date, y =value,group=title1),visible=TRUE)%>%
  hc_navigator(enabled=TRUE)%>%
  hc_rangeSelector(enabled = TRUE,selected =4,inputDateFormat= "%b-%y")%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  )%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
  
```


Inflation & Prices {data-orientation=rows}
================================================================================

Column {data-width=600}
-----------------------------------------------------------------------
### **Consumer-Price index, 12-month change: Selected Sectors**

```{r,message=FALSE,warning=FALSE}

hchart(df6[which(df6$year>2018),], "heatmap",hcaes(x = date , y = title1, value = round(pch12,digits=1)), name = "Index")%>% 
  hc_colorAxis(stops = color_stops(10, rev(RColorBrewer::brewer.pal(10, "RdYlBu")))) %>% 
  hc_title(text = "") %>% 
  hc_legend(layout = "horizontal", verticalAlign = "top", align = "right", valueDecimals = 0)%>%
  hc_yAxis(title="",labels=list(style=list(fontSize="16px", fontWeight = "bold")))%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  ,opposite=TRUE,title="",visible=FALSE)%>%
  hc_tooltip(headerFormat = "{point.title}",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")


```

Column {data-width=400}
-------------------------------------

### **Food, 12-month change**

```{r,message=FALSE}

hchart(df9[which(df9$year>2018),], "heatmap",hcaes(x = date , y = title1, value = round(pch12,digits=1)), name = "Index")%>% 
  hc_title(text = "") %>% 
  hc_legend(layout = "horizontal", verticalAlign = "top", align = "right", valueDecimals = 0)%>%
  hc_yAxis(title="",labels=list(style=list(fontSize="14px", fontWeight = "bold")))%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  ,opposite=TRUE,title="",visible=FALSE)%>%
  hc_tooltip(headerFormat = "{point.title}",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")
```   

### **Energy and Transportation, 12-month change**  

```{r}

hchart(df8[which(df8$year>2018),], "heatmap",hcaes(x = date , y = title1, value = round(pch12,digits=1)), name = "Index")%>% 
  hc_title(text = "") %>% 
  hc_legend(layout = "horizontal", verticalAlign = "top", align = "right", valueDecimals = 0)%>%
  hc_yAxis(title="",labels=list(style=list(fontSize="14px", fontWeight = "bold")))%>%
  hc_add_theme(hc_theme_google())%>%
  hc_xAxis(type = "datetime",
    dateTimeLabelFormats = list(
      month = "%b-%y" # Month name and short year
    )
  ,opposite=TRUE,title="",visible=FALSE)%>%
  hc_tooltip(headerFormat = "{point.title}",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")

```

### **Consumer-Price index, 12-month change(%)**

```{r,message=FALSE,warning=FALSE}
hchart(df7, "line", hcaes(x = date, y =round(pch12,2), group = title1))%>%
  hc_yAxis(title="")%>%
  hc_xAxis(title="")%>% 
  hc_title(text = "")%>%
  hc_navigator(enabled=TRUE)%>%
  hc_tooltip(headerFormat = "",pointFormat = "{point.periodName} {point.year}: <b>{point.value:,.2f}<b>")%>%
  hc_add_theme(hc_theme_google())
  
```